Insert your title here

### 2019-06-12 prod/paper/paper_draft.tex
adding more detail to paper

\section{Introduction}
\label{intro}
Included citations as necessary: ~\cite{Nobody06}
\section{Task and Dataset Description}
\label{sec:task}
The \textit{Humor Analysis based on Humor Annotation (HAHA)} competition asked for analysis of two tasks in the Spanish language based on a coprpus of publicly collected data ~\cite{castro2018crowd}:
\begin{itemize}
\item \textbf{Task1: Humor Detection}:Detemine if a tweet is humorous. System ranking is based on F1 score which will balance precision and accuracy.
\item \textbf{Task2: Funniness Score}:If humorous, what is the average humor rating of the tweet. System ranking is based on RMSE.
\end{itemize}
HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons) and a True/False labels as well as a ``Funninness Score'' that is the average of the 1 to 5 start votes cast.  Examples and data can be found on the CodaLab competition webpage\footnote{http://competitions.codalab.org/competitions/22194/}.

\section{System Description}
\label{sec:system}
We follow the method of ULMFiT ~\cite{DBLP:journals/corr/abs-1801-06146} and train a language model based on a larger corpus.

Since we are working with Twitter data, we collected 475,143 tweets in the spanish lanugage using tweepy ~\cite{tweepy}.
Text with citations \cite{RefB} and \cite{RefJ}.
\subsection{Data and Cleanup}
\label{sec:cleaning}

Using sentencepiece~\cite{DBLP:journals/corr/abs-1808-06226} to parte into sub-word units,

Clean by removing the new-line character \verb|\n| in each of the tweets and replacing with \verb|xxnl|.

Use standard pre-processing rules (show example of cleaned up text):

Original:
\begin{verbatim} 
Saber, entender y estar convencides que la frase 
#LaESILaDefendemosEntreTodes es nuestra linea es nuestro eje.
#AlertaESI!!!!
Vamos por mas!!! e invitamos a todas aquellas personas que quieran 
se parte.
\end{verbatim}

Cleaned up:
\begin{verbatim} 
xxbos saber , entender y estar convencides que la frase 
# laesiladefendemosentretodes es nuestra linea es nuestro eje.
xxnl  # alertaesi xxrep 4 ! xxnl vamos por mas ! ! ! e invitamos a 
todas aquellas personas que quieran se parte.
\end{verbatim}

@@

\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

\section{Experiments and Results}
\label{sec:4}

\section{Conclusion}
\label{sec:4}

@@

% Non-BibTeX users please use
%\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
%\bibitem{RefJ}
% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
%\end{thebibliography}

>>>>

\section{Introduction}
\label{intro}
Included citations as necessary: ~\cite{Nobody06}
\paragraph{Contribution} Our contribution with this work is..

\section{Task and Dataset Description}
\label{sec:task}
The \textit{Humor Analysis based on Humor Annotation (HAHA)} competition asked for analysis of two tasks in the Spanish language based on a coprpus of publicly collected data ~\cite{castro2018crowd}:
\begin{itemize}
\item \textbf{Task1: Humor Detection}:Detemine if a tweet is humorous. System ranking is based on F1 score which will balance precision and accuracy.
\item \textbf{Task2: Funniness Score}:If humorous, what is the average humor rating of the tweet. System ranking is based on RMSE.
\end{itemize}
HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons) and a True/False labels as well as a ``Funninness Score'' that is the average of the 1 to 5 start votes cast.  Examples and data can be found on the CodaLab competition webpage\footnote{http://competitions.codalab.org/competitions/22194/}.

\section{System Description}
\label{sec:system}

We generally follow the method of ULMFiT ~\cite{DBLP:journals/corr/abs-1801-06146}
\begin{enumerate}
	\item Train a language model (LM) on a large corpus of data
	\item Fine-tune the LM based on the target task language data
	\item Replace the final layer of the LM with a softmax or linear output layer and then fine-tune on the particular task at hand (classification or regression)
\end{enumerate}
Below we will give more detail on each step and the parameters used to generate our system.
\subsection{Data, Cleanup \& Tokenization}
\label{sec:datacleaning}
\subsection{Additional Data}
For our initial training, we  collected 475,143 tweets in the Spanish language using tweepy ~\cite{tweepy}.  The vocabulary and frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is used to train.

We combined the labeled and un-labeled text data so that we have the largest corpus of language for our fine-tuning step.

\subsection{Cleaning}
We applied a list of default cleanup functions included in Fastai and added an additional one for this Twitter dataset.
\begin{itemize}
	\item Add spaces between special chars (ie. \verb|!!!| to \verb|! ! !|)
	\item Remove useless spaces (remove more than 2 spaces in sequence)
	\item Replace repetition at the character level (ie. \verb|grrrreat| becomes \verb|g xxrep r 3 eat|)
	\item Replace repition at the word level (similar to above)
	\item Deal with ALL CAPS words replacing with a token and converting to lower case.
	\item \textbf{NEW:} Move all text onto a single line by replacing new-lines inside a tweet with a reserved word (ie. \verb|\n| to \verb|xxnl|)
\end{itemize}

\pagebreak  %move as needed to keep tweet text together
Here is an example of replacing the original tweet with our parsed version.

Original:
\begin{verbatim} 
Saber, entender y estar convencides que la frase \
#LaESILaDefendemosEntreTodes es nuestra linea es nuestro eje.\
#AlertaESI!!!!
Vamos por mas!!! e invitamos a todas aquellas personas que quieran \
se parte.
\end{verbatim}

Cleaned up:
\begin{verbatim} 
xxbos saber , entender y estar convencides que la frase \
# laesiladefendemosentretodes es nuestra linea es nuestro eje.\
xxnl  # alertaesi xxrep 4 ! xxnl vamos por mas ! ! ! e invitamos a \
todas aquellas personas que quieran se parte.
\end{verbatim}

\subsection{Tokenization}
We used sentencepiece~\cite{DBLP:journals/corr/abs-1808-06226} to parse into sub-word units and reduce the possible out-of-vocabulary (OOV) terms in the data set.  We selected a vocab size of 30,000 sub-word units and got 99.95\% character coverage including emojis.

\section{Training and Results}
\label{sec:4}
LM: 10\% validation set for training

@@

\subsection{Random Seed as a Hyperparamter}

\section{Conclusion}
\label{sec:5}

@@
